Statistical Guarantees for Local Spectral Clustering on Random Neighborhood Graphs

### 2021-09-01 jmlr/revision/appendix.tex
Newest version of jmlr tex and bib files.

\documentclass{article}
\usepackage{amsmath, amsfonts, amsthm, amssymb}
\usepackage{xr}
\usepackage[colorlinks]{hyperref}
\usepackage[parfill]{parskip}
\usepackage{algpseudocode}
\usepackage{algorithm}
\usepackage{enumerate}
\usepackage[shortlabels]{enumitem}
\usepackage{graphics}
\usepackage[export]{adjustbox} 
\usepackage{subcaption}
\usepackage{mathtools}
\usepackage{tikz}
\usepackage{verbatim}
\usepackage{fullpage}

\externaldocument{local_spectral_clustering_jmlr_revision_2}

\usepackage{natbib}
\renewcommand{\bibname}{REFERENCES}
\renewcommand{\bibsection}{\subsubsection*{\bibname}}

\DeclareFontFamily{U}{mathx}{\hyphenchar\font45}
\DeclareFontShape{U}{mathx}{m}{n}{<-> mathx10}{}
\DeclareSymbolFont{mathx}{U}{mathx}{m}{n}
\DeclareMathAccent{\wb}{0}{mathx}{"73}

\DeclarePairedDelimiterX{\norm}[1]{\lVert}{\rVert}{#1}
\DeclarePairedDelimiterX{\seminorm}[1]{\lvert}{\rvert}{#1}

% Make a widecheck symbol (thanks, Stack Exchange!)
\DeclareFontFamily{U}{mathx}{\hyphenchar\font45}
\DeclareFontShape{U}{mathx}{m}{n}{
	<5> <6> <7> <8> <9> <10>
	<10.95> <12> <14.4> <17.28> <20.74> <24.88>
	mathx10
}{}
\DeclareSymbolFont{mathx}{U}{mathx}{m}{n}
\DeclareFontSubstitution{U}{mathx}{m}{n}
\DeclareMathAccent{\widecheck}{0}{mathx}{"71}
% widecheck made

\newcommand{\eqdist}{\ensuremath{\stackrel{d}{=}}}
\newcommand{\Graph}{\mathcal{G}}
\newcommand{\Reals}{\mathbb{R}}
\newcommand{\iid}{\overset{\text{i.i.d}}{\sim}}
\newcommand{\convprob}{\overset{p}{\to}}
\newcommand{\convdist}{\overset{w}{\to}}
\newcommand{\Expect}[1]{\mathbb{E}\left[ #1 \right]}
\newcommand{\Risk}[2][P]{\mathcal{R}_{#1}\left[ #2 \right]}
\newcommand{\Prob}[1]{\mathbb{P}\left( #1 \right)}
\newcommand{\iset}{\mathbf{i}}
\newcommand{\jset}{\mathbf{j}}
\newcommand{\myexp}[1]{\exp \{ #1 \}}
\newcommand{\abs}[1]{\left \lvert #1 \right \rvert}
\newcommand{\restr}[2]{\ensuremath{\left.#1\right|_{#2}}}
\newcommand{\ext}[1]{\widetilde{#1}}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\seq}[1]{\set{#1}_{n \in \N}}
\newcommand{\floor}[1]{\left\lfloor #1 \right\rfloor}
\newcommand{\Var}{\mathrm{Var}}
\newcommand{\Cov}{\mathrm{Cov}}
\newcommand{\diam}{\mathrm{diam}}

\newcommand{\emC}{C_n}
\newcommand{\emCpr}{C'_n}
\newcommand{\emCthick}{C^{\sigma}_n}
\newcommand{\emCprthick}{C'^{\sigma}_n}
\newcommand{\emS}{S^{\sigma}_n}
\newcommand{\estC}{\widehat{C}_n}
\newcommand{\hC}{\hat{C^{\sigma}_n}}
\newcommand{\vol}{\mathrm{vol}}
\newcommand{\cut}{\mathrm{cut}}
\newcommand{\spansp}{\mathrm{span}~}
\newcommand{\1}{\mathbf{1}}

\newcommand{\Linv}{L^{\dagger}}
\DeclareMathOperator*{\argmin}{argmin}
\DeclareMathOperator*{\argmax}{argmax}

\newcommand{\emF}{\mathbb{F}_n}
\newcommand{\emG}{\mathbb{G}_n}
\newcommand{\emP}{\mathbb{P}_n}
\newcommand{\F}{\mathcal{F}}
\newcommand{\D}{\mathcal{D}}
\newcommand{\R}{\mathcal{R}}
\newcommand{\Rd}{\Reals^d}
\newcommand{\Nbb}{\mathbb{N}}

%%% Vectors
\newcommand{\thetast}{\theta^{\star}}
\newcommand{\betap}{\beta^{(p)}}
\newcommand{\betaq}{\beta^{(q)}}
\newcommand{\vardeltapq}{\varDelta^{(p,q)}}
\newcommand{\lambdavec}{\boldsymbol{\lambda}}

%%% Matrices
\newcommand{\X}{X} % no bold
\newcommand{\Y}{Y} % no bold
\newcommand{\Z}{Z} % no bold
\newcommand{\Lgrid}{L_{\grid}}
\newcommand{\Dgrid}{D_{\grid}}
\newcommand{\Linvgrid}{L_{\grid}^{\dagger}}
\newcommand{\Lap}{L}
\newcommand{\NLap}{{\bf N}}
\newcommand{\PLap}{{\bf P}}
\newcommand{\Id}{I}

%%% Sets and classes
\newcommand{\Xset}{\mathcal{X}}
\newcommand{\Vset}{\mathcal{V}}
\newcommand{\Sset}{\mathcal{S}}
\newcommand{\Hclass}{\mathcal{H}}
\newcommand{\Pclass}{\mathcal{P}}
\newcommand{\Leb}{L}
\newcommand{\mc}[1]{\mathcal{#1}}
\newcommand{\mbb}[1]{\mathbb{#1}}

%%% Distributions and related quantities
\newcommand{\Pbb}{\mathbb{P}}
\newcommand{\Ebb}{\mathbb{E}}
\newcommand{\Qbb}{\mathbb{Q}}
\newcommand{\Ibb}{\mathbb{I}}

%%% Operators
\newcommand{\Tadj}{T^{\star}}
\newcommand{\dive}{\mathrm{div}}
\newcommand{\dif}{\mathop{}\!\mathrm{d}}
\newcommand{\gradient}{\mathcal{D}}
\newcommand{\Hessian}{\mathcal{D}^2}
\newcommand{\dotp}[2]{\langle #1, #2 \rangle}
\newcommand{\Dotp}[2]{\Bigl\langle #1, #2 \Bigr\rangle}

%%% Misc
\newcommand{\grid}{\mathrm{grid}}
\newcommand{\critr}{R_n}
\newcommand{\dx}{\,dx}
\newcommand{\dy}{\,dy}
\newcommand{\dr}{\,dr}
\newcommand{\dxpr}{\,dx'}
\newcommand{\dypr}{\,dy'}
\newcommand{\wt}[1]{\widetilde{#1}}
\newcommand{\wh}[1]{\widehat{#1}}
\newcommand{\ol}[1]{\wb{#1}}
\newcommand{\spec}{\mathrm{spec}}
\newcommand{\LE}{\mathrm{LE}}
\newcommand{\LS}{\mathrm{LS}}
\newcommand{\SM}{\mathrm{SM}}
\newcommand{\OS}{\mathrm{OS}}
\newcommand{\PLS}{\mathrm{PLS}}

%%% Theorem environments
\newtheorem{theorem}{Theorem}[section]
\newtheorem{conjecture}{Conjecture}[section]
\newtheorem{lemma}{Lemma}[section]
\newtheorem{example}{Example}[section]
\newtheorem{corollary}{Corollary}[section]
\newtheorem{proposition}{Proposition}[section]
\newtheorem{assumption}{Assumption}[section]
\newtheorem{remark}{Remark}[section]

\theoremstyle{definition}
\newtheorem{definition}{Definition}[section]

\theoremstyle{remark}

\begin{document}
\title{Proofs for ``Geometry of Local Spectral Clustering''}
\author{Alden Green}
\date{\today}
\maketitle

The proofs of our major theorems largely consist of (at most) three modular parts.
\begin{enumerate}
	\item \textbf{Fixed graph results.} Results which hold with respect to an arbitrary graph $G$, and are stated with respect to functionals (i.e. normalized cut, conductance, and local spread) of $G$;
	\item \textbf{Sample-to-population results.} For the specific choice $G = G_{n,r}$, we relate the aforementioned functionals to their population analogues. 
	\item \textbf{Bounds on population functionals.} (In the case of density clustering only.) When the candidate cluster is a $\lambda$-density cluster, we bound the population functionals by a function of $\lambda$, as well as the other relevant parameters introduced in Section~\ref{sec:ppr_density_cluster}.
\end{enumerate}
The first three sections of this appendix will correspond to each of these three parts. In Section~\ref{sec:pf_major_theorems}, we will combine these parts to prove the major theorems of our main text, Theorems~\ref{thm:volume_ssd_ub} and~\ref{thm:density_cluster_volume_ssd_ub}, as well as our negative result, Theorem~\ref{thm:ppr_lb}. In Section~\ref{sec:appr_misclassification_error} we derive upper bounds for the aPPR vector, and show that under certain conditions the PPR vector can perfectly separate two density clusters. Finally, in Section~\ref{sec:experimental_details} we give relevant details regarding our experiments.

\section{Fixed graph results}
In this section, we give all results that hold with respect to an arbitrary graph $G$. For the convenience of the reader, we begin by reviewing some notation from the main text, and also introduce some new notation.

@@

\begin{proof}[Proof (of Lemma~\ref{lem:zhu})]
As mentioned in the main text, Lemma~\ref{lem:zhu} is equivalent, up to constants, to Lemma~3.4 in \cite{zhu2013}, and the proof of Lemma~\ref{lem:zhu} proceeds along very similar lines to the proof of that lemma. In fact, we directly use the following three inequalities, derived in that work:
\begin{itemize}
	\item \textbf{(c.f. Lemma 3.2 of \cite{zhu2013})} For any seed node $v \in C$, the PPR vector is lower bounded,
	\begin{equation}
	\label{pf:zhu1}
	\wt{p}_v(u) \geq \frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(\wt{G})\bigr) \cdot \wt{\pi}(u),~~\textrm{for every $u \in C$.}
	\end{equation}
	\item \textbf{(c.f. Corollary 3.3 of \cite{zhu2013})} For any seed node $v \in C$, there exists a so-called leakage distribution $\ell = \ell(v)$ such that $\mathrm{supp}(\ell) \subseteq C$, $\|\ell\|_1 \leq 2\Phi(C;G)/\alpha$, and 
	\begin{equation}
	\label{pf:zhu2}
	p_v(u) \geq \wt{p}_v(u) - \wt{p}_{\ell}(u),~~\textrm{for every $u \in C$.}
	\end{equation}
	\item \textbf{(c.f. Lemma 3.1 of \cite{zhu2013})} There exists a set $C^g \subset C$ with $\vol(C^g;G) \geq \frac{1}{2}\vol(C;G)$ such that for any seed node $v \in C^g$, the following inequality holds
	\begin{equation}
	\label{pf:zhu3}
	p_v(C^c) \leq 2\frac{\Phi(C;G)}{\alpha}.
	\end{equation}
\end{itemize}
We use~\eqref{pf:zhu1}-\eqref{pf:zhu3} to separately upper bound $\vol(S_{\beta,v} \setminus C;G)$, $\vol(C^{\mathrm{int}} \setminus S_{\beta,v};G)$ and $\vol(C^{\mathrm{bdry}} \setminus S_{\beta,v};G)$; here $C^{\mathrm{int}} \cup C^{\mathrm{bdry}} = C$ is a partition of $C$, with
\begin{equation*}
C^{\mathrm{int}} := \Bigl\{u \in C: \deg(u;\wt{G}) > \bigl(1 - \alpha \cdot \beta \cdot \vol(C;G)\bigr) \deg(u;G) \Bigr\},
\end{equation*}
consisting of those vertices $u \in C$ with sufficient large degree in $\wt{G}$.

@@

Finally, we upper bound $\vol(C^{\mathrm{bdry}} \setminus S_{\beta,v};G)$. Indeed, for any $u \in C^{\mathrm{bdry}}$,
\begin{equation*}
\frac{1}{\vol(C;G)}\sum_{w \not\in C} \1((u,w) \in E) \geq \alpha \cdot \beta \cdot \deg(u;G)
\end{equation*}
and summing over all such vertices yields
\begin{equation}
\label{pf:zhu6}
\vol(C^{\mathrm{bdry}};G) \leq \frac{1}{\alpha \beta \vol(C;G)}\sum_{\substack{u \in C^{\mathrm{bdry}} \\ w \not\in C}} \1((u,w) \in E) \leq \frac{\Phi(C;G)}{\alpha \cdot \beta}.
\end{equation} 
The claim follows upon summing the upper bounds in~\eqref{pf:zhu3.5}, \eqref{pf:zhu5} and~\eqref{pf:zhu6}.
\end{proof}

If the cluster estimate $\wh{C}$ is instead obtained by sweep cutting the aPPR vector $p_v^{(\varepsilon)}$, a similar upper bound on $\vol(\wh{C} \vartriangle C)$ holds, provided that $\varepsilon$ is sufficiently small.
\begin{corollary}
	\label{cor:zhu}
	For a set $C \subseteq V$, suppose that $\alpha,\beta$ satisfy~\eqref{eqn:zhu_condition}, and additionally that 
	\begin{equation}
	\label{eqn:zhu_condition_2}
	\varepsilon \leq \frac{1}{25\vol(C;G)}.
	\end{equation}
	Then there exists a set $C^g \subset C$ with $\vol(C^g;G) \geq \frac{1}{2}\vol(C^g;G)$ such that for any $v \in C^g$, the sweep cut $S_{\beta,v}$ of the aPPR vector $p_v^{(\varepsilon)}$ satisfies
	\begin{equation}
	\label{eqn:zhu_ub}
	\vol(S_{\beta,v} \vartriangle C;G) \leq 6\frac{\Phi(C;G)}{\alpha \beta}.
	\end{equation}
\end{corollary}
\begin{proof}[Proof (of Corollary~\ref{cor:zhu})]
	Recall that the upper bound~\eqref{eqn:zhu_ub} on $\vol(\wh{C} \vartriangle C;G)$ comes from combining the upper bounds on $\vol(\wh{C} \setminus C;G)$, $\vol(C^{\mathrm{int}} \setminus \wh{C};G)$ and $\vol(C^{\mathrm{bdry}} \setminus \wh{C};G)$ in~\eqref{pf:zhu3.5},~\eqref{pf:zhu5} and~\eqref{pf:zhu6}. From the upper bound $p_v^{(\varepsilon)}(u) \leq p_v(u)$ for all $u \in V$, it is clear that both~\eqref{pf:zhu3.5} and~\eqref{pf:zhu6} continue to hold when the aPPR vector is used instead of the PPR vector.

	It remains only to establish an upper bound on~$\vol(C^{\mathrm{int}} \setminus \wh{C};G)$. For any $u \in C \setminus S_{\beta,v}$, from inequality~\eqref{pf:zhu2} and the lower bound $p_v^{(\varepsilon)}(u) \geq p_v(u)  - \varepsilon \deg(u;G)$ in~\eqref{eqn:appr_error} we deduce that
	\begin{equation}
	\frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(\wt{G})\bigr) \cdot \wt{\pi}(u) -  (\beta + \varepsilon)\deg(u;G) \leq \wt{p}_{\ell}(u).
	\end{equation}
	Following the same steps as used in the proof of Lemma~\ref{lem:zhu} yields the following inequality:
	\begin{equation*}
	\biggl(\frac{3(1 - \alpha \beta \vol(C;G))\cdot\bigl(1 - \alpha \tau_{\infty}(\wt{G})\bigr)}{4\vol(C;G)} - \beta\biggr) \cdot \vol\bigl(C^{\mathrm{int}} \setminus S_{\beta,v}; G\bigr) \leq \wt{p}_{\ell}\bigl(C^{\mathrm{int}} \setminus S_{\beta,v}\bigr) \leq 2\frac{\Phi(C;G)}{\alpha}.
	\end{equation*}
	The upper bounds on $\alpha,\beta$ in~\eqref{eqn:zhu_condition},  and on $\varepsilon$ in~\eqref{eqn:zhu_condition_2}, imply that
	\begin{equation*}
	\biggl(\frac{3(1 - \alpha \beta \vol(C;G))\cdot\bigl(1 - \alpha \tau_{\infty}(\wt{G})\bigr)}{4\vol(C;G)} - \beta\biggr) \geq \frac{2}{3}\beta,
	\end{equation*}
	and we conclude that
	\begin{equation}
	\label{pf:zhu2_1}
	\vol(C^{\mathrm{int}} \setminus S_{\beta,v}; G) \leq \frac{3\Phi(C;G)}{\alpha\beta}.
	\end{equation}
	Summing the right hand sides of~\eqref{pf:zhu2},~\eqref{pf:zhu6}, and~\eqref{pf:zhu2_1} yields the claim.
\end{proof}

@@

\begin{proof}[Proof (of Lemma~\ref{lem:ppr_uniform_bound})]
	We first show~\eqref{eqn:ppr_uniform_bound_C}. From~\eqref{pf:zhu3} and~\eqref{pf:zhu2}, we have that
	\begin{equation*}
	p_v(u) \geq \frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(\wt{G})\bigr) \cdot \wt{\pi}(u) - \wt{p}_{\ell}(u)~~\textrm{for all $u \in C$,}
	\end{equation*}
	where $\ell$ has support $\mathrm{supp}(\ell) \subseteq C$ with $\|\ell\|_1 \leq 2\Phi(C;G)/\alpha$. Recalling that $u \in C_{o}$ implies that $u \not\in \mathrm{supp}(C_{o})$, as a consequence of~\eqref{pf:interpolator_bound_max_entry}, 
	\begin{equation*}
	\wt{p}_{\ell}(u) \leq \frac{\|\ell\|_1}{d_{\min}(\wt{G})}~~\textrm{for all $u \in C_{o}$,}
	\end{equation*}
	establishing~\eqref{eqn:ppr_uniform_bound_C}. The proof of~\eqref{eqn:ppr_uniform_bound_Cprime} follows similarly:
	\begin{equation*}
	p_v(u) = p_s(u) \overset{(i)}{\leq} \frac{\|s\|_1}{d_{\min}(C';G)} = \frac{\|\ell\|_1}{d_{\min}(C';G)},~~\textrm{for all $u \in C_{o}'$},
	\end{equation*}
	where the presence of $d_{\min}(C';G)$ on the right hand side of $(i)$ can be verified by inspecting~\eqref{pf:interpolator_bound_max_entry_inductive_step}. 	
\end{proof}

@@

	\textbf{Case 2.} Otherwise one of $k_j - 2 \Psi(G) \wb{k}_j$ or $k_j + 2 \Psi(G) \wb{k}_j$ is not in $[K_0,2m  - K_0]$. Without loss of generality assume $k_j < m$, so that (i) we have $k_j - 2 \Psi(G) \wb{k}_j < K_0$ and (ii) $k_j + (k_j - K_0) \leq 2m - K_0$. We deduce the following:
	\begin{align*}
	h^{(t)}(k_j) & \overset{(\textrm{i})}{\leq} \frac{1}{2}\Bigl(h^{(t - 1)}(K_0) + h^{(t - 1)}\bigl(k_j + (k_j - K_0)\bigr)\Bigr) \\
	& \overset{(\textrm{ii})}{\leq} \frac{1}{2}\Bigl(h^{(t_0)}(K_0) + h^{(t)}\bigl(k_j + (k_j - K_0)\bigr)\Bigr) \\
	& \overset{(\textrm{iii})}{\leq}\frac{1}{2}\Bigl(L_{K_0}(K_0;h^{(t_0)}) + L_{K_0}(2k_j - K_0; h^{(t_0)}\bigr) + C(K_0;h^{(t_0)})\sqrt{\wb{2k_j - K_0}}\left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0 - 1}\Bigr) \\
	& \leq L_{K_0}(k_j; h^{(t_0)}) + C(K_0;h^{(t_0)}) \frac{\sqrt{2\wb{k}_j}}{2} \left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0 - 1} \\
	& \leq L_{K_0}(k_j;h^{(t_0)}) + C(K_0;h^{(t_0)}) \sqrt{\wb{k}_j} \cdot \left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0}
	\end{align*}
	where $(\textrm{(i)})$ follows from~\eqref{pf:mixing_random_walk_inductive_step_h} and the concavity of $h^{(t - 1)}$,  we deduce $(\textrm{ii})$ from~\eqref{pf:mixing_random_walk_inductive_step_h}, which implies that $h^{(t)}(k) \leq h^{(t_0)}(k)$, and $(\textrm{iii})$ follows from applying the inductive hypothesis to $h^{(t - 1)}(2k_j - K_0)$. 	
\end{proof}

\begin{proof}[Proof (of Lemma~\ref{lem:mixing_time_PPR}).]
	We will show that if $\Phi(S_j; g) \geq \phi$ for each $j = 1,\ldots,n$, then \eqref{eqn:mixing_time_PPR} holds for all $t$ and any $k \in [K_0,2m - K_0]$.

@@

\begin{proof}[Proof (of Proposition~\ref{prop:conductance_lb_transportation_distance})]

@@

\end{proof}

@@

\begin{proof}[Proof (of Lemma~\ref{lem:uniform_density_cluster_conductance})]
	For ease of notation, throughout this proof we write $\wt{\nu}$ for the uniform probability measure over $\mc{C}_{\lambda,\sigma}$, put $\ell \nu_d r^d := \min_{x \in \mc{C}_{\lambda,\sigma}}\nu(B(x,r) \cap \mc{C}_{\sigma})$ and $a := r/(2\rho L)$.

@@

\clearpage
\bibliographystyle{plainnat}
\bibliography{../../local_spectral_bibliography}

\end{document}

>>>>

\noindent The proofs of our major theorems largely consist of (at most) three modular parts.
\begin{enumerate}
	\item \textbf{Fixed graph results.} Results which hold with respect to an arbitrary graph $G$, and are stated with respect to functionals (i.e. normalized cut, conductance, and local spread) of $G$;
	\item \textbf{Sample-to-population results.} For the specific choice $G = G_{n,r}$, w  e relate the aforementioned functionals to their population analogues. 
	\item \textbf{Bounds on population functionals.} (In the case of density clustering only.) When the candidate cluster is a $\lambda$-density cluster, we bound the population functionals by a function of $\lambda$, as well as the other relevant parameters introduced in Section~\ref{sec:ppr_density_cluster}.
\end{enumerate}

Appendices \ref{apdx:fixed_graph}-\ref{apdx:density_cluster_population_functionals} will correspond to each of these three parts. In Appendix~\ref{apdx:pf_major_theorems}, we will combine these parts to prove the major theorems of our main text, Theorems~\ref{thm:volume_ssd_ub} and~\ref{thm:density_cluster_volume_ssd_ub}, as well as our negative result, Theorem~\ref{thm:ppr_lb}. In Appendix~\ref{apdx:appr_misclassification_error} we derive upper bounds for the aPPR vector, and show that under certain conditions the PPR vector can perfectly separate two density clusters. Finally, in Appendix~\ref{apdx:experimental_details} we give relevant details regarding our experiments.

\section{Fixed graph results}
\label{apdx:fixed_graph}
In this appendix, we give all results that hold with respect to an arbitrary graph $G$. For the convenience of the reader, we begin by reviewing some notation from the main text, and also introduce some new notation.

@@

\paragraph{Proof of Lemma~\ref{lem:zhu}.}
As mentioned in the main text, Lemma~\ref{lem:zhu} is equivalent, up to constants, to Lemma~3.4 in \cite{zhu2013}, and the proof of Lemma~\ref{lem:zhu} proceeds along very similar lines to the proof of that lemma. In fact, we directly use the following three inequalities, derived in that work:
\begin{itemize}
	\item \textbf{(c.f. Lemma 3.2 of \cite{zhu2013})} For any seed node $v \in C$, the PPR vector is lower bounded,
	\begin{equation}
	\label{pf:zhu1}
	\wt{p}_v(u) \geq \frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(\wt{G})\bigr) \cdot \wt{\pi}(u),~~\textrm{for every $u \in C$.}
	\end{equation}
	\item \textbf{(c.f. Corollary 3.3 of \cite{zhu2013})} For any seed node $v \in C$, there exists a so-called leakage distribution $\ell = \ell(v)$ such that $\mathrm{supp}(\ell) \subseteq C$, $\|\ell\|_1 \leq 2\Phi(C;G)/\alpha$, and 
	\begin{equation}
	\label{pf:zhu2}
	p_v(u) \geq \wt{p}_v(u) - \wt{p}_{\ell}(u),~~\textrm{for every $u \in C$.}
	\end{equation}
	\item \textbf{(c.f. Lemma 3.1 of \cite{zhu2013})} There exists a set $C^g \subset C$ with $\vol(C^g;G) \geq \frac{1}{2}\vol(C;G)$ such that for any seed node $v \in C^g$, the following inequality holds
	\begin{equation}
	\label{pf:zhu3}
	p_v(C^c) \leq 2\frac{\Phi(C;G)}{\alpha}.
	\end{equation}
\end{itemize}
teWe use~\eqref{pf:zhu1}-\eqref{pf:zhu3} to separately upper bound $\vol(S_{\beta,v} \setminus C;G)$, $\vol(C^{\mathrm{int}} \setminus S_{\beta,v};G)$ and $\vol(C^{\mathrm{bdry}} \setminus S_{\beta,v};G)$; here $C^{\mathrm{int}} \cup C^{\mathrm{bdry}} = C$ is a partition of $C$, with
\begin{equation*}
C^{\mathrm{int}} := \Bigl\{u \in C: \deg(u;\wt{G}) > \bigl(1 - \alpha \cdot \beta \cdot \vol(C;G)\bigr) \deg(u;G) \Bigr\},
\end{equation*}
consisting of those vertices $u \in C$ with sufficient large degree in $\wt{G}$.

@@

Finally, we upper bound $\vol(C^{\mathrm{bdry}} \setminus S_{\beta,v};G)$. Indeed, for any $u \in C^{\mathrm{bdry}}$,
\begin{equation*}
\frac{1}{\vol(C;G)}\sum_{w \not\in C} \1((u,w) \in E) \geq \alpha \cdot \beta \cdot \deg(u;G)
\end{equation*}
and summing over all such vertices yields
\begin{equation}
\label{pf:zhu6}
\vol(C^{\mathrm{bdry}};G) \leq \frac{1}{\alpha \beta \vol(C;G)}\sum_{\substack{u \in C^{\mathrm{bdry}} \\ w \not\in C}} \1((u,w) \in E) \leq \frac{\Phi(C;G)}{\alpha \cdot \beta}.
\end{equation} 
The claim follows upon summing the upper bounds in~\eqref{pf:zhu3.5}, \eqref{pf:zhu5} and~\eqref{pf:zhu6}.

If the cluster estimate $\wh{C}$ is instead obtained by sweep cutting the aPPR vector $p_v^{(\varepsilon)}$, a similar upper bound on $\vol(\wh{C} \vartriangle C)$ holds, provided that $\varepsilon$ is sufficiently small.
\begin{corollary}
	\label{cor:zhu}
	For a set $C \subseteq V$, suppose that $\alpha,\beta$ satisfy~\eqref{eqn:zhu_condition}, and additionally that 
	\begin{equation}
	\label{eqn:zhu_condition_2}
	\varepsilon \leq \frac{1}{25\vol(C;G)}.
	\end{equation}
	Then there exists a set $C^g \subset C$ with $\vol(C^g;G) \geq \frac{1}{2}\vol(C^g;G)$ such that for any $v \in C^g$, the sweep cut $S_{\beta,v}$ of the aPPR vector $p_v^{(\varepsilon)}$ satisfies
	\begin{equation}
	\label{eqn:zhu_ub_appr}
	\vol(S_{\beta,v} \vartriangle C;G) \leq 6\frac{\Phi(C;G)}{\alpha \beta}.
	\end{equation}
\end{corollary}

\paragraph{Proof of Corollary~\ref{cor:zhu}.}
	Recall that the upper bound~\eqref{eqn:zhu_ub} on $\vol(\wh{C} \vartriangle C;G)$ comes from combining the upper bounds on $\vol(\wh{C} \setminus C;G)$, $\vol(C^{\mathrm{int}} \setminus \wh{C};G)$ and $\vol(C^{\mathrm{bdry}} \setminus \wh{C};G)$ in~\eqref{pf:zhu3.5},~\eqref{pf:zhu5} and~\eqref{pf:zhu6}. From the upper bound $p_v^{(\varepsilon)}(u) \leq p_v(u)$ for all $u \in V$, it is clear that both~\eqref{pf:zhu3.5} and~\eqref{pf:zhu6} continue to hold when the aPPR vector is used instead of the PPR vector.

	It remains only to establish an upper bound on~$\vol(C^{\mathrm{int}} \setminus \wh{C};G)$. For any $u \in C \setminus S_{\beta,v}$, from inequality~\eqref{pf:zhu2} and the lower bound $p_v^{(\varepsilon)}(u) \geq p_v(u)  - \varepsilon \deg(u;G)$ in~\eqref{eqn:appr_error} we deduce that
	\begin{equation}
	\frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(\wt{G})\bigr) \cdot \wt{\pi}(u) -  (\beta + \varepsilon)\deg(u;G) \leq \wt{p}_{\ell}(u).
	\end{equation}
	Following the same steps as used in the proof of Lemma~\ref{lem:zhu} yields the following inequality:
	\begin{equation*}
	\biggl(\frac{3(1 - \alpha \beta \vol(C;G))\cdot\bigl(1 - \alpha \tau_{\infty}(\wt{G})\bigr)}{4\vol(C;G)} - \beta\biggr) \cdot \vol\bigl(C^{\mathrm{int}} \setminus S_{\beta,v}; G\bigr) \leq \wt{p}_{\ell}\bigl(C^{\mathrm{int}} \setminus S_{\beta,v}\bigr) \leq 2\frac{\Phi(C;G)}{\alpha}.
	\end{equation*}
	The upper bounds on $\alpha,\beta$ in~\eqref{eqn:zhu_condition},  and on $\varepsilon$ in~\eqref{eqn:zhu_condition_2}, imply that
	\begin{equation*}
	\biggl(\frac{3(1 - \alpha \beta \vol(C;G))\cdot\bigl(1 - \alpha \tau_{\infty}(\wt{G})\bigr)}{4\vol(C;G)} - \beta\biggr) \geq \frac{2}{3}\beta,
	\end{equation*}
	and we conclude that
	\begin{equation}
	\label{pf:zhu2_1}
	\vol(C^{\mathrm{int}} \setminus S_{\beta,v}; G) \leq \frac{3\Phi(C;G)}{\alpha\beta}.
	\end{equation}
	Summing the right hand sides of~\eqref{pf:zhu2},~\eqref{pf:zhu6}, and~\eqref{pf:zhu2_1} yields the claim.

@@

\paragraph{Proof of Lemma~\ref{lem:ppr_uniform_bound}.}
	We first show~\eqref{eqn:ppr_uniform_bound_C}. From~\eqref{pf:zhu3} and~\eqref{pf:zhu2}, we have that
	\begin{equation*}
	p_v(u) \geq \frac{3}{4}\bigl(1 - \alpha \cdot \tau_{\infty}(\wt{G})\bigr) \cdot \wt{\pi}(u) - \wt{p}_{\ell}(u)~~\textrm{for all $u \in C$,}
	\end{equation*}
	where $\ell$ has support $\mathrm{supp}(\ell) \subseteq C$ with $\|\ell\|_1 \leq 2\Phi(C;G)/\alpha$. Recalling that $u \in C_{o}$ implies that $u \not\in \mathrm{supp}(C_{o})$, as a consequence of~\eqref{pf:interpolator_bound_max_entry}, 
	\begin{equation*}
	\wt{p}_{\ell}(u) \leq \frac{\|\ell\|_1}{d_{\min}(\wt{G})}~~\textrm{for all $u \in C_{o}$,}
	\end{equation*}
	establishing~\eqref{eqn:ppr_uniform_bound_C}. The proof of~\eqref{eqn:ppr_uniform_bound_Cprime} follows similarly:
	\begin{equation*}
	p_v(u) = p_s(u) \overset{(i)}{\leq} \frac{\|s\|_1}{d_{\min}(C';G)} = \frac{\|\ell\|_1}{d_{\min}(C';G)},~~\textrm{for all $u \in C_{o}'$},
	\end{equation*}
	where the presence of $d_{\min}(C';G)$ on the right hand side of $(i)$ can be verified by inspecting~\eqref{pf:interpolator_bound_max_entry_inductive_step}.

@@

	\textbf{Case 2.} Otherwise one of $k_j - 2 \Psi(G) \wb{k}_j$ or $k_j + 2 \Psi(G) \wb{k}_j$ is not in $[K_0,2m  - K_0]$. Without loss of generality assume $k_j < m$, so that (i) we have $k_j - 2 \Psi(G) \wb{k}_j < K_0$ and (ii) $k_j + (k_j - K_0) \leq 2m - K_0$. We deduce the following:
	\begin{align*}
	h^{(t)}(k_j) & \overset{(\textrm{i})}{\leq} \frac{1}{2}\Bigl(h^{(t - 1)}(K_0) + h^{(t - 1)}\bigl(k_j + (k_j - K_0)\bigr)\Bigr) \\
	& \overset{(\textrm{ii})}{\leq} \frac{1}{2}\Bigl(h^{(t_0)}(K_0) + h^{(t)}\bigl(k_j + (k_j - K_0)\bigr)\Bigr) \\
	& \overset{(\textrm{iii})}{\leq}\frac{1}{2}\Bigl(L_{K_0}(K_0;h^{(t_0)}) + L_{K_0}(2k_j - K_0; h^{(t_0)}\bigr) + C(K_0;h^{(t_0)})\sqrt{\wb{2k_j - K_0}}\left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0 - 1}\Bigr) \\
	& \leq L_{K_0}(k_j; h^{(t_0)}) + C(K_0;h^{(t_0)}) \frac{\sqrt{2\wb{k}_j}}{2} \left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0 - 1} \\
	& \leq L_{K_0}(k_j;h^{(t_0)}) + C(K_0;h^{(t_0)}) \sqrt{\wb{k}_j} \cdot \left(1 - \frac{\Psi(G)^2}{8}\right)^{t - t_0}
	\end{align*}
	where $(\textrm{(i)})$ follows from~\eqref{pf:mixing_random_walk_inductive_step_h} and the concavity of $h^{(t - 1)}$,  we deduce $(\textrm{ii})$ from~\eqref{pf:mixing_random_walk_inductive_step_h}, which implies that $h^{(t)}(k) \leq h^{(t_0)}(k)$, and $(\textrm{iii})$ follows from applying the inductive hypothesis to $h^{(t - 1)}(2k_j - K_0)$.

\paragraph{Proof (of Lemma~\ref{lem:mixing_time_PPR}).}
	We will show that if $\Phi(S_j; g) \geq \phi$ for each $j = 1,\ldots,n$, then \eqref{eqn:mixing_time_PPR} holds for all $t$ and any $k \in [K_0,2m - K_0]$.

@@

\paragraph{Proof of Proposition~\ref{prop:conductance_lb_transportation_distance}.}

@@

@@

\paragraph{Proof of Lemma~\ref{lem:uniform_density_cluster_conductance}.}
	For ease of notation, throughout this proof we write $\wt{\nu}$ for the uniform probability measure over $\mc{C}_{\lambda,\sigma}$, put $\ell \nu_d r^d := \min_{x \in \mc{C}_{\lambda,\sigma}}\nu(B(x,r) \cap \mc{C}_{\sigma})$ and $a := r/(2\rho L)$.

@@
